---
title: "Cthulhu Update 2"
output: 
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(dplyr)
library(data.table)
library(Rmisc)
library(ggplot2)
library(cowplot)
library(ez)
library(lme4)
library(tidyverse)
library(scales)
library(gdata)
library(quickpsy)
library(afex)
library(ggrepel)
source("https://raw.githubusercontent.com/janhove/janhove.github.io/master/RCode/sortLvls.R")
theme_set(theme_bw())
options(scipen=999)
load("df.Rdata")
```

## Comparing pre-test and post-test
________
```{r,include=FALSE}
# subset to just discrimination blocks
discrim <- subset(df,grepl("discrimination",block))

# remove session 4
discrim <- subset(discrim,session!=4)

# subset vowel
discrim.vowel <- subset(discrim,session!="S3")

# create variable to combine forwards/backwards discrimination steps
discrim.vowel$discrim.token <- ifelse(discrim.vowel$fname=="i-y-u_step1-step1.wav","1-1",
                               ifelse(discrim.vowel$fname=="i-y-u_step2-step2.wav","2-2",
                               ifelse(discrim.vowel$fname=="i-y-u_step3-step3.wav","3-3",
                               ifelse(discrim.vowel$fname=="i-y-u_step4-step4.wav","4-4",
                               ifelse(discrim.vowel$fname=="i-y-u_step5-step5.wav","5-5",
                               ifelse(discrim.vowel$fname=="i-y-u_step6-step6.wav","6-6",
                               ifelse(discrim.vowel$fname=="i-y-u_step7-step7.wav","7-7",
                               ifelse(discrim.vowel$fname=="i-y-u_step_1-step_3.wav","1-3",
                               ifelse(discrim.vowel$fname=="i-y-u_step_2-step_4.wav","2-4",
                               ifelse(discrim.vowel$fname=="i-y-u_step_3-step_5.wav","3-5",
                               ifelse(discrim.vowel$fname=="i-y-u_step_4-step_6.wav","4-6",
                               ifelse(discrim.vowel$fname=="i-y-u_step_5-step_7.wav","5-7",
                               ifelse(discrim.vowel$fname=="i-y-u_step_3-step_1.wav","1-3",
                               ifelse(discrim.vowel$fname=="i-y-u_step_4-step_2.wav","2-4",
                               ifelse(discrim.vowel$fname=="i-y-u_step_5-step_3.wav","3-5",
                               ifelse(discrim.vowel$fname=="i-y-u_step_6-step_4.wav","4-6",
                               ifelse(discrim.vowel$fname=="i-y-u_step_7-step_5.wav","5-7",NA)))))))))))))))))


discrim.vowel$condition <- ifelse(discrim.vowel$discrim.token=="1-1","same",
                           ifelse(discrim.vowel$discrim.token=="2-2","same",
                           ifelse(discrim.vowel$discrim.token=="3-3","same",
                           ifelse(discrim.vowel$discrim.token=="4-4","same",
                           ifelse(discrim.vowel$discrim.token=="5-5","same",
                           ifelse(discrim.vowel$discrim.token=="6-6","same",
                           ifelse(discrim.vowel$discrim.token=="7-7","same",
                           ifelse(discrim.vowel$discrim.token=="1-3","different",
                           ifelse(discrim.vowel$discrim.token=="2-4","different",
                           ifelse(discrim.vowel$discrim.token=="3-5","different",
                           ifelse(discrim.vowel$discrim.token=="4-6","different",
                           ifelse(discrim.vowel$discrim.token=="5-7","different",NA))))))))))))

# subset only post-test
# discrim.vowel.pretest <- subset(discrim.vowel,grepl("pretest",block))
# discrim.vowel <- subset(discrim.vowel,grepl("posttest",block))

  # d’ averaging across stimuli ======

# make a new data frame that contains the data we need
dprime.average <- discrim.vowel %>%
  group_by(session,subject2,condition,block) %>%
  summarize(prop_cor=mean(correct_response))

# calculate hits and false alarms on different trials
dprime.average <- dprime.average %>% mutate(prop_cor=ifelse(condition=="different",prop_cor,1-prop_cor))
dprime.average <- spread(dprime.average, condition, prop_cor)
colnames(dprime.average) <- c("Session","Subject","Block","Hit","FA")

# we will use this closure to create two functions: one to change 1 to .99 and 
# one to change 0 to .01 (.99 and .01 still have to be specified though)
cutoff <- function(value) {
  function(x,y) {
    x[x == value] <- y
    x
  }
}

cutoff_1 <- cutoff(1)
cutoff_0 <- cutoff(0)

dprime.average$Hit <- cutoff_1(dprime.average$Hit,.99)
dprime.average$Hit <- cutoff_0(dprime.average$Hit,.01)
dprime.average$FA <- cutoff_1(dprime.average$FA,.99)
dprime.average$FA <- cutoff_0(dprime.average$FA,.01)

# make function for d', then apply it to each time point, participant, etc.
d_prime <- function(Hit, FA){
  qnorm(Hit) - qnorm(FA)
}

dprime <- dprime.average %>%
  group_by(Session,Subject,Block) %>%
  mutate(dprime = d_prime(Hit,FA))

dprime <- dprime %>% select(-c(Hit,FA))

# create dprime by session figure 
dprime_cllpsd <- ddply(dprime,.(Session),summarize,mean=mean(dprime))
colnames(dprime_cllpsd)[2] <- "dprime"

ggplot(dprime,aes(x=Session,y=dprime)) + 
  geom_bar(data=dprime_cllpsd,stat="identity",position="dodge",aes(fill=Session),alpha=0.7) +
  geom_point(aes(color=Session),position = position_dodge(width=0.75)) +
  scale_y_continuous('d Prime',breaks=c(0,.25,.5,.75,1,1.25,1.5,1.75,2,2.25,2.5,2.75),labels=c(0,.25,.5,.75,1,1.25,1.5,1.75,2,2.25,2.5,2.75)) +
  scale_x_discrete('Session',labels=c('1','2','3')) +
  scale_fill_brewer('Session #',palette="Purples") +
  scale_color_brewer('Session #',palette="Purples") +
  theme_dark() +
  theme(text = element_text(size=20))

ggplot(dprime,aes(x=Session,y=dprime)) + 
  geom_boxplot(position="dodge",aes(fill=Session),middle=mean(dprime$dprime)) +
  geom_point(position = position_dodge(width=0.75)) +
  scale_y_continuous('d Prime',breaks=c(-.1,0,0.5,1,1.5,2,2.50,3),labels=c(-.1,0,0.5,1,1.5,2,2.50,3)) +
  scale_x_discrete('Session',labels=c('1','2','3')) +
  scale_fill_brewer('Session #',palette = "Purples") +
  scale_color_brewer('Session #',palette="Purples") +
  theme_dark() +
  theme(text = element_text(size=20))

  # d' for each stimulus ====

# make a new data frame that contains the data we need

dprime.stimulus <- discrim.vowel %>%
  group_by(session,subject2,condition,discrim.token,block) %>%
  summarize(prop_cor = mean(correct_response))

dprime.stimulus <- dprime.stimulus %>% mutate(prop_incor=1-prop_cor)

# we will use this closure to create two functions: one to change 1 to .99 and 
# one to change 0 to .01 (.99 and .01 still have to be specified though)
cutoff <- function(value) {
  function(x,y) {
    x[x == value] <- y
    x
  }
}

cutoff_1 <- cutoff(1)
cutoff_0 <- cutoff(0)

dprime.stimulus$prop_cor <- cutoff_1(dprime.stimulus$prop_cor,.99)
dprime.stimulus$prop_cor <- cutoff_0(dprime.stimulus$prop_cor,.01)
dprime.stimulus$prop_incor <- cutoff_1(dprime.stimulus$prop_incor,.99)
dprime.stimulus$prop_incor <- cutoff_0(dprime.stimulus$prop_incor,.01)

### 1-3 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="1-1" | dprime.stimulus$discrim.token=="3-3")
dprime_temp_same <- ddply(dprime_temp_same,.(session,subject2,block),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="1-3")
dprime_temp_different <- ddply(dprime_temp_different,.(session,subject2,block),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp1_3 <- rbind(dprime_temp_same,dprime_temp_different)
  
d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp1_3 <- spread(dprime_temp1_3, condition, mean)

dprime_temp1_3 <- dprime_temp1_3 %>%
  group_by(session,subject2,block) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp1_3$stimulus <- "1-3"

### 2-4 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="2-2" | dprime.stimulus$discrim.token=="4-4")
dprime_temp_same <- ddply(dprime_temp_same,.(session,subject2,block),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="2-4")
dprime_temp_different <- ddply(dprime_temp_different,.(session,subject2,block),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp2_4 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp2_4 <- spread(dprime_temp2_4, condition, mean)

dprime_temp2_4 <- dprime_temp2_4 %>%
  group_by(session,subject2,block) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp2_4$stimulus <- "2-4"

### 3-5 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="3-3" | dprime.stimulus$discrim.token=="5-5")
dprime_temp_same <- ddply(dprime_temp_same,.(session,subject2,block),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="3-5")
dprime_temp_different <- ddply(dprime_temp_different,.(session,subject2,block),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp3_5 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp3_5 <- spread(dprime_temp3_5, condition, mean)

dprime_temp3_5 <- dprime_temp3_5 %>%
  group_by(session,subject2,block) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp3_5$stimulus <- "3-5"

### 4-6 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="4-4" | dprime.stimulus$discrim.token=="6-6")
dprime_temp_same <- ddply(dprime_temp_same,.(session,subject2,block),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="4-6")
dprime_temp_different <- ddply(dprime_temp_different,.(session,subject2,block),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp4_6 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp4_6 <- spread(dprime_temp4_6, condition, mean)

dprime_temp4_6 <- dprime_temp4_6 %>%
  group_by(session,subject2,block) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp4_6$stimulus <- "4-6"

### 5-7 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="5-5" | dprime.stimulus$discrim.token=="7-7")
dprime_temp_same <- ddply(dprime_temp_same,.(session,subject2,block),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="5-7")
dprime_temp_different <- ddply(dprime_temp_different,.(session,subject2,block),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp5_7 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp5_7 <- spread(dprime_temp5_7, condition, mean)

dprime_temp5_7 <- dprime_temp5_7 %>%
  group_by(session,subject2,block) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp5_7$stimulus <- "5-7"

dprime_id <- data.frame()
dprime_id <- rbind(dprime_temp1_3,dprime_temp2_4,dprime_temp3_5,dprime_temp4_6,dprime_temp5_7)
rm(dprime_temp_same,dprime_temp_different,dprime_temp1_3,dprime_temp2_4,dprime_temp3_5,dprime_temp4_6,dprime_temp5_7)

# create dprime by stimulus figure 
# boxplot
# ggplot(dprime_id,aes(x=stimulus,y=dprime)) + 
#   geom_boxplot(position="dodge",aes(fill=session)) +
#   scale_fill_brewer('Session #',palette = "Purples") +
#   theme_dark() +
#   theme(text = element_text(size=20))

# lineplot group average
dprime_lineplot <- summarySE(dprime_id, measurevar="dprime",groupvars = c("session","stimulus","block"))
dprime_lineplot$plotting <- ifelse(dprime_lineplot$session==1&dprime_lineplot$block=="pretest_discrimination",1,
                                   ifelse(dprime_lineplot$session==2&dprime_lineplot$block=="pretest_discrimination",2,
                                          ifelse(dprime_lineplot$session==3&dprime_lineplot$block=="pretest_discrimination",3,
                                                 ifelse(dprime_lineplot$session==1&dprime_lineplot$block=="posttest_discrimination",4,
                                                        ifelse(dprime_lineplot$session==2&dprime_lineplot$block=="posttest_discrimination",5,
                                                               ifelse(dprime_lineplot$session==3&dprime_lineplot$block=="posttest_discrimination",6,""))))))

peak.discrim <- dprime_id %>% group_by(subject2,session,block) %>% slice(which.max(dprime))
peak.discrim <- select(peak.discrim,"session","subject2","dprime","stimulus","block")

# combine with category boundaries
load("boundaries.Rda")

# create figure before rounding boundaries
ggplot(boundaries,aes(x=session,y=Boundary,group=factor(subject2)),label=subject2) + 
  geom_point(size=3) +
  geom_line(aes(group=factor(subject2),color=factor(subject2)),size=1.5) +
  geom_label_repel(label=boundaries$subject2) +
  scale_color_discrete(guide=F) +
  ylim(0,7) +
  theme(text = element_text(size=20))

# mixed effects model
bound.model <- mixed(Boundary ~ session + (1|subject2),data=boundaries)
bound.model

# round boundaries
boundaries <- boundaries[rep(1:nrow(boundaries),2),]
boundaries$block[1:78] <- "pretest_discrimination"
boundaries$block[1.1:78.1] <- "posttest_discrimination"
boundaries$Boundary <- round(boundaries$Boundary)

# look at peak discrim token and boundaries
peak.discrim$boundary <- boundaries$Boundary
peak.discrim <- subset(peak.discrim,boundary!=-8)
ggplot(peak.discrim,aes(x=stimulus,y=boundary,color=session,label=subject2)) + 
  scale_y_continuous('boundary') +
  ylim(0,7) + xlab('Peak discrimination stimulus') + geom_label_repel(aes(label=subject2,color=session)) +
  theme(text = element_text(size=20))

# use this information to determine what is between-category and what is within-category
dprime_id$boundary <- NA
for (i in unique(dprime_id$subject2)){
  for (s in unique(dprime_id$session)){
    temp.boundaries <- boundaries[boundaries$subject2==i & boundaries$session==s,"Boundary"]
    dprime_id$boundary <- ifelse(dprime_id$subject2==i & dprime_id$session==s,temp.boundaries,dprime_id$boundary)
  }
}

dprime_id$discrim.type <- ifelse(dprime_id$boundary==0&dprime_id$stimulus=="3-5","BC","WC")
dprime_id$discrim.type <- ifelse(dprime_id$boundary==-8&dprime_id$stimulus=="3-5","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==1&dprime_id$stimulus=="1-3","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==2&dprime_id$stimulus=="1-3","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==3&dprime_id$stimulus=="2-4","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==4&dprime_id$stimulus=="3-5","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==5&dprime_id$stimulus=="4-6","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==6&dprime_id$stimulus=="5-7","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==7&dprime_id$stimulus=="5-7","BC",dprime_id$discrim.type)

dprime.relative.bound <- data.frame(matrix(vector(), 0, 10,
                                           dimnames=list(c(),c("session","subject2","block", "FA", "Hit","dprime",
                                                               "stimulus","boundary","discrim.type","relative.bound"))))

for (subj in unique(dprime_id$subject2)){
  for(ses in unique(dprime_id$session)){
    temp <- subset(dprime_id,subject2==subj&session==ses)
    B.C. = dprime_id[dprime_id$subject2==subj&dprime_id$discrim.type=="BC"&dprime_id$session==ses,"stimulus"]
    if (B.C.[1,1]=="1-3"){
      temp$relative.bound <- ifelse(temp$stimulus=="1-3"&temp$discrim.type=="BC","BC",
                                       ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC+1",
                                              ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC+2",
                                                     ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+3",
                                                            ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+4","")))))
    } else if (B.C.[1,1]=="2-4"){
      temp$relative.bound <- ifelse(temp$stimulus=="2-4"&temp$discrim.type=="BC","BC",
                                       ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-1",
                                              ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC+1",
                                                     ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+2",
                                                            ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+3","")))))
    } else if (B.C.[1,1]=="3-5"){
      temp$relative.bound <- ifelse(temp$stimulus=="3-5"&temp$discrim.type=="BC","BC",
                                       ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-2",
                                              ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC-1",
                                                     ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+1",
                                                            ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+2","")))))
    } else if (B.C.[1,1]=="4-6"){
      temp$relative.bound <- ifelse(temp$stimulus=="4-6"&temp$discrim.type=="BC","BC",
                                       ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-3",
                                              ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC-2",
                                                     ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC-1",
                                                            ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+1","")))))
    } else if (B.C.[1,1]=="5-7"){
      temp$relative.bound <- ifelse(temp$stimulus=="5-7"&temp$discrim.type=="BC","BC",
                                       ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-2",
                                              ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC-1",
                                                     ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC+1",
                                                            ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+2","")))))
    }
    temp <- as.data.frame(temp)
    dprime.relative.bound <- rbind(dprime.relative.bound,temp)
  }
}

dprime_rb_lineplot <- summarySE(dprime.relative.bound, measurevar="dprime",groupvars = c("session","relative.bound","block"))
dprime_rb_lineplot$relative.bound <- factor(dprime_rb_lineplot$relative.bound,levels=c("WC-3","WC-2","WC-1","BC","WC+1","WC+2","WC+3","WC+4"))
dprime_rb_lineplot$plotting <- ifelse(dprime_rb_lineplot$session==1&dprime_rb_lineplot$block=="pretest_discrimination",1,
                                   ifelse(dprime_rb_lineplot$session==2&dprime_rb_lineplot$block=="pretest_discrimination",2,
                                          ifelse(dprime_rb_lineplot$session==3&dprime_rb_lineplot$block=="pretest_discrimination",3,
                                                 ifelse(dprime_rb_lineplot$session==1&dprime_rb_lineplot$block=="posttest_discrimination",4,
                                                        ifelse(dprime_rb_lineplot$session==2&dprime_rb_lineplot$block=="posttest_discrimination",5,
                                                               ifelse(dprime_rb_lineplot$session==3&dprime_rb_lineplot$block=="posttest_discrimination",6,""))))))                                                                     
```

### d' figure including block:
```{r,echo=FALSE,warning = FALSE,fig.width=8,fig.height=6}
ggplot(dprime_lineplot,aes(x=stimulus,y=dprime,group=plotting,color=session)) +
  geom_point(aes(color=session),stat='summary', fun.y='mean', size=3.5) +
  geom_line(aes(color=session,linetype=block),stat='summary', fun.y='mean', size=2) +
  geom_errorbar(aes(ymin=dprime-se,ymax=dprime+se,color=session),width=.25,size=1.25) +
  scale_color_brewer('Session',palette="Set1") +
  scale_linetype_discrete('Block',labels=c("Post-test","Pre-test")) +
  theme(text = element_text(size=20))
```



### d' figure including block using relative boundary:
```{r,echo=FALSE,warning = FALSE,fig.width=8,fig.height=6}
ggplot(dprime_rb_lineplot,aes(x=relative.bound,y=dprime,group=plotting,color=session)) +
  geom_point(aes(color=session),stat='summary', fun.y='mean', size=3.5) +
  geom_line(aes(color=session,linetype=block),stat='summary', fun.y='mean', size=2) +
  geom_errorbar(aes(ymin=dprime-se,ymax=dprime+se,color=session),width=.25,size=1.25) +
  scale_color_brewer('Session',palette="Set1") +
  scale_linetype_discrete('Block',labels=c("Post-test","Pre-test")) +
  theme(text = element_text(size=20))
```



### Mixed effects model on d' with relative boundary restricted to middle tokens:
Models that include the outliers cause fatal issues with convergence because of the lack of data at certain interaction terms. Excluding "WC-3" and "WC+4" fixes these issues.

```{r,include=FALSE}
dp.rel.mid <- subset(dprime.relative.bound,relative.bound!="WC-3"&relative.bound!="WC+4")
dp.rel.mid$session <- as.factor(dp.rel.mid$session)
dp.rel.mid$relative.bound <- as.factor(dp.rel.mid$relative.bound)
dp.rel.mid$block <- as.factor(dp.rel.mid$block)

# lmem.relative.bound.mid1 <- mixed(dprime ~ relative.bound*session*block + (block|subject2) + (session|subject2),data=dp.rel.mid,expand_re = TRUE,
#                                  control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 150000))) doesn't converge

# lmem.relative.bound.mid2 <- mixed(dprime ~ relative.bound*session*block + (block||subject2) + (session||subject2),data=dp.rel.mid,expand_re = TRUE,
#                                   control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 150000))) doesn't converge

lmem.relative.bound.mid3 <- mixed(dprime ~ relative.bound*session*block + (session||subject2),data=dp.rel.mid,expand_re = TRUE,
                                  control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 150000)))
lmem.relative.bound.mid4 <- mixed(dprime ~ relative.bound*session*block + (block||subject2),data=dp.rel.mid,expand_re = TRUE,
                                  control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 150000)))
lmem.relative.bound.mid5 <- mixed(dprime ~ relative.bound*session*block + (1|subject2),data=dp.rel.mid,expand_re = TRUE,
                                  control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 150000)))

anova(lmem.relative.bound.mid3,lmem.relative.bound.mid4,lmem.relative.bound.mid5)
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
lmem.relative.bound.mid3
summary(lmem.relative.bound.mid3)
```

###  Mixed effects model on d' with non-relative boundary:
Showing the effect of block with an acoustic boundary as opposed to an individually-derived one.
```{r,include=FALSE}
dprime.relative.bound$nonrelative.bound <- ifelse(dprime.relative.bound$stimulus=="2-4"|dprime.relative.bound$stimulus=="3-5","BC","WC")

dprime.relative.bound$session <- as.factor(dprime.relative.bound$session)
dprime.relative.bound$nonrelative.bound <- as.factor(dprime.relative.bound$nonrelative.bound)
dprime.relative.bound$block <- as.factor(dprime.relative.bound$block)

# lmem.nonrelative.bound1 <- mixed(dprime ~ nonrelative.bound*session*block + (block|subject2) + (session|subject2),data=dprime.relative.bound,expand_re = TRUE,
#                                  control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 150000)))
# lmem.nonrelative.bound2 <- mixed(dprime ~ nonrelative.bound*session*block + (block||subject2) + (session||subject2),data=dprime.relative.bound,expand_re = TRUE,
#                                  control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 150000)))

lmem.nonrelative.bound3 <- mixed(dprime ~ nonrelative.bound*session*block + (session||subject2),data=dprime.relative.bound,expand_re = TRUE,
                                 control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 150000)))
lmem.nonrelative.bound4 <- mixed(dprime ~ nonrelative.bound*session*block + (block||subject2),data=dprime.relative.bound,expand_re = TRUE,
                                 control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 150000)))
lmem.nonrelative.bound5 <- mixed(dprime ~ nonrelative.bound*session*block + (1|subject2),data=dprime.relative.bound,expand_re = TRUE,
                                 control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 150000)))

anova(lmem.nonrelative.bound3,lmem.nonrelative.bound4,lmem.nonrelative.bound5)
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
lmem.nonrelative.bound3
```

## Sinewave token analyses
___

### Looking at training data:
```{r,include=FALSE}
# separate training data
training <- subset(df,grepl("training",block))

# remove session 4
training <- subset(training,session!=4)

# subset vowel training
training.sine <- subset(training,session=="S3")

# calculate error bars
training.sine.stats <- summarySE(data=training.sine, measurevar="correct_response",groupvars=c("subject2","block"))

# calculate number of blocks completed
training.sine.stats$blocks.complete <- ifelse(training.sine.stats$N<62,1,
                                         ifelse(training.sine.stats$N>61&training.sine.stats$N<120,2,
                                                ifelse(training.sine.stats$N>120&training.sine.stats$N<182,3,NA)))
# summarize
training.sine.avg <- ddply(training.sine.stats,.(block,blocks.complete),summarize,mean=mean(correct_response))

#bar graph
ggplot(training.sine.stats,aes(x=block,y=correct_response)) + 
  geom_bar(stat="summary",position="dodge",fun.y='mean') +
  scale_y_continuous('Percent accuracy',breaks=c(0,0.25,0.5,0.75,1),labels=c(0,25,50,75,100)) +
  scale_x_discrete('Training block',labels=c('Easy 1-7','Medium 2-6','Hard 3-5')) +
  theme(text = element_text(size=20))

# overlay individual data points and group mean bars
id <- ddply(training.sine.stats,.(subject2,block,blocks.complete),summarize,mean=mean(correct_response))
stats <- summarySE(data=training.sine.stats, measurevar="correct_response",groupvars=("block"))
gd <- select(stats,block,correct_response)
gd <- rename(gd,mean=correct_response)
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# across session
ggplot(id,aes(x=block,y=mean)) +
  geom_point(aes(x=block,shape=factor(blocks.complete)),position = position_dodge(width=1)) + 
  geom_bar(data=gd,stat="identity",alpha=0.5,position="dodge") +
  scale_y_continuous('Percent accuracy',breaks=c(0,0.25,0.5,0.75,1),labels=c(0,25,50,75,100)) +
  scale_x_discrete('Training level',labels=c('Easy 1-7','Medium 2-6','Hard 3-5')) +
  scale_shape_discrete('Training\nblock\nrepetitions') +
  coord_cartesian(ylim=c(0.4,1)) +
  theme(text=element_text(size=20))
```

### Mixed-effects model for Sine training data:
```{r,include=FALSE}
training.sine$block <- as.factor(training.sine$block)
training.sine$subject2 <- as.factor(training.sine$subject2)

afex.training.model.sine <- mixed(correct_response ~ block + (1|subject2), family=binomial(link="logit"),data=training.sine,method="LRT")
```

```{r,echo = FALSE, message = FALSE, warning = FALSE}
afex.training.model.sine
summary(afex.training.model.sine)
```


### Looking at phonetic categorization boundaries:
```{r,include=FALSE}
# subset continuum data
continuum <- subset(df,df$block=="continuum")

# subset sine sessions
continuum_sine <- subset(continuum,continuum$session=="S3")

# drop NA trials and trials where people hit the wrong button
continuum_sine <- subset(continuum_sine,continuum_sine$response!="None")
continuum_sine <- subset(continuum_sine,continuum_sine$response!="d")
continuum_sine$response <- tolower(continuum_sine$response)

# create binary response variable
continuum_sine$cb <- ifelse(continuum_sine$subject2==3|continuum_sine$subject2==11|
                              continuum_sine$subject2==15|continuum_sine$subject2==20|continuum_sine$subject2==31,"cb1","cb2")
continuum_sineCB1 <- subset(continuum_sine,continuum_sine$cb=="cb1")
continuum_sineCB2 <- subset(continuum_sine,continuum_sine$cb=="cb2")
continuum_sineCB1$resp1 <- ifelse(continuum_sineCB1$response=="a",1,0)
continuum_sineCB2$resp1 <- ifelse(continuum_sineCB2$response=="a",0,1)
continuum_sine <- rbind(continuum_sineCB1,continuum_sineCB2)

# create 'step' variable
continuum_sine$step <- substr(continuum_sine$fname,9,9)

stats_sine <- summarySE(continuum_sine, measurevar="resp1",groupvars = c("subject2","step"))
```

```{r,echo = FALSE, message = FALSE, warning = FALSE}
ggplot(stats_sine, aes(x=as.numeric(step),y=resp1)) +
  geom_point(stat='summary', fun.y='mean', size=2.5,color="grey") +
  geom_line(stat='summary', fun.y='mean', size=0.75,color="grey") +
  geom_errorbar(aes(ymin=resp1-se,ymax=resp1+se),width=.5) +
  facet_wrap(~subject2) +
  scale_x_continuous('/i/ to /y/ continuum step', breaks=c(1:7)) +
  scale_y_continuous('Percent /y/ responses', breaks=c(0,0.25,0.5,0.75,1), labels=c(0,25,50,75,100)) +
  coord_cartesian(ylim=c(0,1)) + 
  theme(text = element_text(size=20))
```

#### Histogram of boundaries:
```{r,echo = FALSE, message = FALSE, warning = FALSE}
# combine with category boundaries
load("sine.boundaries.Rda")
# create figure before rounding boundaries
ggplot(sine.boundaries,aes(x=Boundary,group=factor(subject2))) + 
  geom_histogram(binwidth=.5) +
  theme(text = element_text(size=20))
```

### Sine d' by stimulus:
```{r,include=FALSE}
discrim <- subset(df,grepl("discrimination",block))

# remove session 4
discrim <- subset(discrim,session!=4)

# subset vowel
discrim.sine <- subset(discrim,session=="S3")

# create variable to combine forwards/backwards discrimination steps
discrim.sine$discrim.token <- ifelse(discrim.sine$fname=="iyu_step_1-step_1.wav","1-1",
                                      ifelse(discrim.sine$fname=="iyu_step_2-step_2.wav","2-2",
                                             ifelse(discrim.sine$fname=="iyu_step_3-step_3.wav","3-3",
                                                    ifelse(discrim.sine$fname=="iyu_step_4-step_4.wav","4-4",
                                                           ifelse(discrim.sine$fname=="iyu_step_5-step_5.wav","5-5",
                                                                  ifelse(discrim.sine$fname=="iyu_step_6-step_6.wav","6-6",
                                                                         ifelse(discrim.sine$fname=="iyu_step_7-step_7.wav","7-7",
                                                                                ifelse(discrim.sine$fname=="iyu_step_1-step_3.wav","1-3",
                                                                                       ifelse(discrim.sine$fname=="iyu_step_2-step_4.wav","2-4",
                                                                                              ifelse(discrim.sine$fname=="iyu_step_3-step_5.wav","3-5",
                                                                                                     ifelse(discrim.sine$fname=="iyu_step_4-step_6.wav","4-6",
                                                                                                            ifelse(discrim.sine$fname=="iyu_step_5-step_7.wav","5-7",
                                                                                                                   ifelse(discrim.sine$fname=="iyu_step_3-step_1.wav","1-3",
                                                                                                                          ifelse(discrim.sine$fname=="iyu_step_4-step_2.wav","2-4",
                                                                                                                                 ifelse(discrim.sine$fname=="iyu_step_5-step_3.wav","3-5",
                                                                                                                                        ifelse(discrim.sine$fname=="iyu_step_6-step_4.wav","4-6",
                                                                                                                                               ifelse(discrim.sine$fname=="iyu_step_7-step_5.wav","5-7",NA)))))))))))))))))


discrim.sine$condition <- ifelse(discrim.sine$discrim.token=="1-1","same",
                                  ifelse(discrim.sine$discrim.token=="2-2","same",
                                         ifelse(discrim.sine$discrim.token=="3-3","same",
                                                ifelse(discrim.sine$discrim.token=="4-4","same",
                                                       ifelse(discrim.sine$discrim.token=="5-5","same",
                                                              ifelse(discrim.sine$discrim.token=="6-6","same",
                                                                     ifelse(discrim.sine$discrim.token=="7-7","same",
                                                                            ifelse(discrim.sine$discrim.token=="1-3","different",
                                                                                   ifelse(discrim.sine$discrim.token=="2-4","different",
                                                                                          ifelse(discrim.sine$discrim.token=="3-5","different",
                                                                                                 ifelse(discrim.sine$discrim.token=="4-6","different",
                                                                                                        ifelse(discrim.sine$discrim.token=="5-7","different",NA))))))))))))


dprime.stimulus <- discrim.sine %>%
  group_by(subject2,condition,discrim.token,block) %>%
  summarize(prop_cor = mean(correct_response))

dprime.stimulus <- dprime.stimulus %>% mutate(prop_incor=1-prop_cor)

# we will use this closure to create two functions: one to change 1 to .99 and 
# one to change 0 to .01 (.99 and .01 still have to be specified though)
cutoff <- function(value) {
  function(x,y) {
    x[x == value] <- y
    x
  }
}

cutoff_1 <- cutoff(1)
cutoff_0 <- cutoff(0)

dprime.stimulus$prop_cor <- cutoff_1(dprime.stimulus$prop_cor,.99)
dprime.stimulus$prop_cor <- cutoff_0(dprime.stimulus$prop_cor,.01)
dprime.stimulus$prop_incor <- cutoff_1(dprime.stimulus$prop_incor,.99)
dprime.stimulus$prop_incor <- cutoff_0(dprime.stimulus$prop_incor,.01)

### 1-3 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="1-1" | dprime.stimulus$discrim.token=="3-3")
dprime_temp_same <- ddply(dprime_temp_same,.(subject2,block),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="1-3")
dprime_temp_different <- ddply(dprime_temp_different,.(subject2,block),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp1_3 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp1_3 <- spread(dprime_temp1_3, condition, mean)

dprime_temp1_3 <- dprime_temp1_3 %>%
  group_by(subject2,block) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp1_3$stimulus <- "1-3"

### 2-4 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="2-2" | dprime.stimulus$discrim.token=="4-4")
dprime_temp_same <- ddply(dprime_temp_same,.(subject2,block),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="2-4")
dprime_temp_different <- ddply(dprime_temp_different,.(subject2,block),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp2_4 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp2_4 <- spread(dprime_temp2_4, condition, mean)

dprime_temp2_4 <- dprime_temp2_4 %>%
  group_by(subject2,block) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp2_4$stimulus <- "2-4"

### 3-5 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="3-3" | dprime.stimulus$discrim.token=="5-5")
dprime_temp_same <- ddply(dprime_temp_same,.(subject2,block),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="3-5")
dprime_temp_different <- ddply(dprime_temp_different,.(subject2,block),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp3_5 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp3_5 <- spread(dprime_temp3_5, condition, mean)

dprime_temp3_5 <- dprime_temp3_5 %>%
  group_by(subject2,block) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp3_5$stimulus <- "3-5"

### 4-6 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="4-4" | dprime.stimulus$discrim.token=="6-6")
dprime_temp_same <- ddply(dprime_temp_same,.(subject2,block),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="4-6")
dprime_temp_different <- ddply(dprime_temp_different,.(subject2,block),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp4_6 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp4_6 <- spread(dprime_temp4_6, condition, mean)

dprime_temp4_6 <- dprime_temp4_6 %>%
  group_by(subject2,block) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp4_6$stimulus <- "4-6"

### 5-7 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="5-5" | dprime.stimulus$discrim.token=="7-7")
dprime_temp_same <- ddply(dprime_temp_same,.(subject2,block),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="5-7")
dprime_temp_different <- ddply(dprime_temp_different,.(subject2,block),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp5_7 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp5_7 <- spread(dprime_temp5_7, condition, mean)

dprime_temp5_7 <- dprime_temp5_7 %>%
  group_by(subject2,block) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp5_7$stimulus <- "5-7"

dprime_id <- data.frame()
dprime_id <- rbind(dprime_temp1_3,dprime_temp2_4,dprime_temp3_5,dprime_temp4_6,dprime_temp5_7)
rm(dprime_temp_same,dprime_temp_different,dprime_temp1_3,dprime_temp2_4,dprime_temp3_5,dprime_temp4_6,dprime_temp5_7)

# create dprime by stimulus figure 
# boxplot
# ggplot(dprime_id,aes(x=stimulus,y=dprime)) + 
#   geom_boxplot(position="dodge",aes(fill=session)) +
#   scale_fill_brewer('Session #',palette = "Purples") +
#   theme_dark() +
#   theme(text = element_text(size=20))

# lineplot group average
dprime_lineplot <- summarySE(dprime_id, measurevar="dprime",groupvars = c("stimulus","block"))

# Sine peak discrim -------------------------------------------------------
peak.discrim <- dprime_id %>% group_by(subject2,block) %>% slice(which.max(dprime))
peak.discrim <- select(peak.discrim,"subject2","dprime","stimulus","block")

# combine with category boundaries
load("sine.boundaries.Rda")

# create figure before rounding boundaries
ggplot(sine.boundaries,aes(x=Boundary,group=factor(subject2))) + 
  geom_histogram(binwidth=.5) +
  theme(text = element_text(size=20))

# round boundaries
sine.boundaries <- sine.boundaries[rep(1:nrow(sine.boundaries),2),]
sine.boundaries$block[1:26] <- "pretest_discrimination"
sine.boundaries$block[1.1:26.1] <- "posttest_discrimination"
sine.boundaries$Boundary <- round(sine.boundaries$Boundary)

# look at peak discrim token and boundaries
peak.discrim$boundary <- sine.boundaries$Boundary
peak.discrim <- subset(peak.discrim,boundary!=-9)
```

```{r,echo = FALSE, message = FALSE, warning = FALSE,fig.width=8,fig.height=6}
ggplot(dprime_lineplot,aes(x=stimulus,y=dprime,group=block)) +
  geom_point(stat='summary', fun.y='mean', size=3.5) +
  geom_line(aes(linetype=block),stat='summary', fun.y='mean', size=2) +
  geom_errorbar(aes(ymin=dprime-se,ymax=dprime+se,linetype=block),width=.25,size=1.25) +
  scale_linetype_discrete('Block',labels=c("Post-test","Pre-test")) +
  theme(text = element_text(size=20))
```


### Boundary locations for participants compared to the peak d' stimulus
```{r,echo = FALSE, message = FALSE, warning = FALSE,fig.width=8,fig.height=6}
ggplot(peak.discrim,aes(x=stimulus,y=boundary,label=subject2)) + 
  scale_y_continuous('Boundary') +
  ylim(0,7) + xlab('Peak discrimination stimulus') + geom_label_repel(aes(label=subject2)) +
  theme(text = element_text(size=20))
```

### Relative boundary for Sine discrmination figure:
```{r,include=FALSE}
# use this information to determine what is between-category and what is within-category
dprime_id$boundary <- NA
for (i in unique(dprime_id$subject2)){
    temp.boundaries <- sine.boundaries[sine.boundaries$subject2==i,"Boundary"]
    dprime_id$boundary <- ifelse(dprime_id$subject2==i,temp.boundaries,dprime_id$boundary)
}


dprime_id$discrim.type <- ifelse(dprime_id$boundary==0&dprime_id$stimulus=="3-5","BC","WC")
dprime_id$discrim.type <- ifelse(dprime_id$boundary==9&dprime_id$stimulus=="3-5","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==1&dprime_id$stimulus=="1-3","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==2&dprime_id$stimulus=="1-3","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==3&dprime_id$stimulus=="2-4","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==4&dprime_id$stimulus=="3-5","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==5&dprime_id$stimulus=="4-6","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==6&dprime_id$stimulus=="5-7","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==7&dprime_id$stimulus=="5-7","BC",dprime_id$discrim.type)
# create figure where discrim tokens are labeled relative to the individuals boundary
dprimesine.relative.bound <- data.frame(matrix(vector(), 0,9,
                                           dimnames=list(c(),c("subject2","block", "FA", "Hit","dprime",
                                                               "stimulus","boundary","discrim.type","relative.bound"))))

for (subj in unique(dprime_id$subject2)){
  for (b in unique(dprime_id$block)){
    temp <- subset(dprime_id,subject2==subj&block==b)
    B.C. = dprime_id[dprime_id$subject2==subj&dprime_id$block==b&dprime_id$discrim.type=="BC","stimulus"]
    if (B.C.[1,1]=="1-3"){
      temp$relative.bound <- ifelse(temp$stimulus=="1-3"&temp$discrim.type=="BC","BC",
                                    ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC+1",
                                           ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC+2",
                                                  ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+3",
                                                         ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+4","")))))
    } else if (B.C.[1,1]=="2-4"){
      temp$relative.bound <- ifelse(temp$stimulus=="2-4"&temp$discrim.type=="BC","BC",
                                    ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-1",
                                           ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC+1",
                                                  ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+2",
                                                         ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+3","")))))
    } else if (B.C.[1,1]=="3-5"){
      temp$relative.bound <- ifelse(temp$stimulus=="3-5"&temp$discrim.type=="BC","BC",
                                    ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-2",
                                           ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC-1",
                                                  ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+1",
                                                         ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+2","")))))
    } else if (B.C.[1,1]=="4-6"){
      temp$relative.bound <- ifelse(temp$stimulus=="4-6"&temp$discrim.type=="BC","BC",
                                    ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-3",
                                           ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC-2",
                                                  ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC-1",
                                                         ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+1","")))))
    } else if (B.C.[1,1]=="5-7"){
      temp$relative.bound <- ifelse(temp$stimulus=="5-7"&temp$discrim.type=="BC","BC",
                                    ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-2",
                                           ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC-1",
                                                  ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC+1",
                                                         ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+2","")))))
    }
    temp <- as.data.frame(temp)
    dprimesine.relative.bound <- rbind(dprimesine.relative.bound,temp)
  }
}

dprime_rb_lineplot <- summarySE(dprimesine.relative.bound, measurevar="dprime",groupvars = c("relative.bound","block"))
dprime_rb_lineplot$relative.bound <- factor(dprime_rb_lineplot$relative.bound,levels=c("WC-3","WC-2","WC-1","BC","WC+1","WC+2","WC+3","WC+4"))
```

```{r,echo = FALSE, message = FALSE, warning = FALSE,fig.width=8,fig.height=6}
ggplot(dprime_rb_lineplot,aes(x=relative.bound,y=dprime,group=block)) +
  geom_point(stat='summary', fun.y='mean', size=3.5) +
  geom_line(aes(linetype=block),stat='summary', fun.y='mean', size=2) +
  geom_errorbar(aes(ymin=dprime-se,ymax=dprime+se),width=.25,size=1.25) +
  scale_linetype_discrete('Block',labels=c("Post-test","Pre-test")) +
  theme(text = element_text(size=20))
```
