---
title: "Cthulhu Update"
output: 
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(dplyr)
library(data.table)
library(Rmisc)
library(ggplot2)
library(cowplot)
library(ez)
library(lme4)
library(tidyverse)
library(scales)
library(gdata)
library(quickpsy)
library(afex)
library(ggrepel)
source("https://raw.githubusercontent.com/janhove/janhove.github.io/master/RCode/sortLvls.R")
theme_set(theme_bw())

load("df.Rdata")

training <- subset(df,grepl("training",block))
training <- subset(training,session!=4)
training.vowel <- subset(training,session!="S3")
training.vowel$block <- as.factor(training.vowel$block)
training.vowel$session <- as.factor(training.vowel$session)
training.vowel$subject2 <- as.factor(training.vowel$subject2)
```

## Training Data Analysis

Mixed-effects model performed on training data with training level (easy, medium, and hard) and session as fixed-effects, and by-subject random slopes and intercepts for block and session as random effects:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
afex.training.model <- mixed(correct_response ~ block*session + (1|subject2), family=binomial(link="logit"),data=training.vowel,method="LRT")
afex.training.model
```

Here is the model looking at the interactions:

```{r, echo = FALSE}
training.model3 <- glmer(correct_response ~ block*session +
                           (block||subject2) + (session||subject2),
                         data=training.vowel,family='binomial',
                         control = glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
summary(training.model3)
```

## Looking at discrimination performance with a relative boundary:
```{r,include=FALSE}
# subset to just discrimination blocks
discrim <- subset(df,grepl("discrimination",block))

# remove session 4
discrim <- subset(discrim,session!=4)

# subset vowel
discrim.vowel <- subset(discrim,session!="S3")

# subset only post-test
discrim.vowel <- subset(discrim.vowel,grepl("posttest",block))

# create variable to combine forwards/backwards discrimination steps
discrim.vowel$discrim.token <- ifelse(discrim.vowel$fname=="i-y-u_step1-step1.wav","1-1",
                               ifelse(discrim.vowel$fname=="i-y-u_step2-step2.wav","2-2",
                               ifelse(discrim.vowel$fname=="i-y-u_step3-step3.wav","3-3",
                               ifelse(discrim.vowel$fname=="i-y-u_step4-step4.wav","4-4",
                               ifelse(discrim.vowel$fname=="i-y-u_step5-step5.wav","5-5",
                               ifelse(discrim.vowel$fname=="i-y-u_step6-step6.wav","6-6",
                               ifelse(discrim.vowel$fname=="i-y-u_step7-step7.wav","7-7",
                               ifelse(discrim.vowel$fname=="i-y-u_step_1-step_3.wav","1-3",
                               ifelse(discrim.vowel$fname=="i-y-u_step_2-step_4.wav","2-4",
                               ifelse(discrim.vowel$fname=="i-y-u_step_3-step_5.wav","3-5",
                               ifelse(discrim.vowel$fname=="i-y-u_step_4-step_6.wav","4-6",
                               ifelse(discrim.vowel$fname=="i-y-u_step_5-step_7.wav","5-7",
                               ifelse(discrim.vowel$fname=="i-y-u_step_3-step_1.wav","1-3",
                               ifelse(discrim.vowel$fname=="i-y-u_step_4-step_2.wav","2-4",
                               ifelse(discrim.vowel$fname=="i-y-u_step_5-step_3.wav","3-5",
                               ifelse(discrim.vowel$fname=="i-y-u_step_6-step_4.wav","4-6",
                               ifelse(discrim.vowel$fname=="i-y-u_step_7-step_5.wav","5-7",NA)))))))))))))))))


discrim.vowel$condition <- ifelse(discrim.vowel$discrim.token=="1-1","same",
                           ifelse(discrim.vowel$discrim.token=="2-2","same",
                           ifelse(discrim.vowel$discrim.token=="3-3","same",
                           ifelse(discrim.vowel$discrim.token=="4-4","same",
                           ifelse(discrim.vowel$discrim.token=="5-5","same",
                           ifelse(discrim.vowel$discrim.token=="6-6","same",
                           ifelse(discrim.vowel$discrim.token=="7-7","same",
                           ifelse(discrim.vowel$discrim.token=="1-3","different",
                           ifelse(discrim.vowel$discrim.token=="2-4","different",
                           ifelse(discrim.vowel$discrim.token=="3-5","different",
                           ifelse(discrim.vowel$discrim.token=="4-6","different",
                           ifelse(discrim.vowel$discrim.token=="5-7","different",NA))))))))))))

# make a new data frame that contains the data we need

dprime.stimulus <- discrim.vowel %>%
  group_by(session,subject2,condition,discrim.token) %>%
  summarize(prop_cor = mean(correct_response))

dprime.stimulus <- dprime.stimulus %>% mutate(prop_incor=1-prop_cor)

# we will use this closure to create two functions: one to change 1 to .99 and 
# one to change 0 to .01 (.99 and .01 still have to be specified though)
cutoff <- function(value) {
  function(x,y) {
    x[x == value] <- y
    x
  }
}

cutoff_1 <- cutoff(1)
cutoff_0 <- cutoff(0)

dprime.stimulus$prop_cor <- cutoff_1(dprime.stimulus$prop_cor,.99)
dprime.stimulus$prop_cor <- cutoff_0(dprime.stimulus$prop_cor,.01)
dprime.stimulus$prop_incor <- cutoff_1(dprime.stimulus$prop_incor,.99)
dprime.stimulus$prop_incor <- cutoff_0(dprime.stimulus$prop_incor,.01)

### 1-3 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="1-1" | dprime.stimulus$discrim.token=="3-3")
dprime_temp_same <- ddply(dprime_temp_same,.(session,subject2),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="1-3")
dprime_temp_different <- ddply(dprime_temp_different,.(session,subject2),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp1_3 <- rbind(dprime_temp_same,dprime_temp_different)
  
d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp1_3 <- spread(dprime_temp1_3, condition, mean)

dprime_temp1_3 <- dprime_temp1_3 %>%
  group_by(session,subject2) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp1_3$stimulus <- "1-3"

### 2-4 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="2-2" | dprime.stimulus$discrim.token=="4-4")
dprime_temp_same <- ddply(dprime_temp_same,.(session,subject2),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="2-4")
dprime_temp_different <- ddply(dprime_temp_different,.(session,subject2),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp2_4 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp2_4 <- spread(dprime_temp2_4, condition, mean)

dprime_temp2_4 <- dprime_temp2_4 %>%
  group_by(session,subject2) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp2_4$stimulus <- "2-4"

### 3-5 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="3-3" | dprime.stimulus$discrim.token=="5-5")
dprime_temp_same <- ddply(dprime_temp_same,.(session,subject2),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="3-5")
dprime_temp_different <- ddply(dprime_temp_different,.(session,subject2),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp3_5 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp3_5 <- spread(dprime_temp3_5, condition, mean)

dprime_temp3_5 <- dprime_temp3_5 %>%
  group_by(session,subject2) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp3_5$stimulus <- "3-5"

### 4-6 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="4-4" | dprime.stimulus$discrim.token=="6-6")
dprime_temp_same <- ddply(dprime_temp_same,.(session,subject2),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="4-6")
dprime_temp_different <- ddply(dprime_temp_different,.(session,subject2),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp4_6 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp4_6 <- spread(dprime_temp4_6, condition, mean)

dprime_temp4_6 <- dprime_temp4_6 %>%
  group_by(session,subject2) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp4_6$stimulus <- "4-6"

### 5-7 ###
dprime_temp_same <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="5-5" | dprime.stimulus$discrim.token=="7-7")
dprime_temp_same <- ddply(dprime_temp_same,.(session,subject2),summarize,mean=mean(prop_incor))
dprime_temp_same$condition <- "FA"
dprime_temp_different <- subset(dprime.stimulus,dprime.stimulus$discrim.token=="5-7")
dprime_temp_different <- ddply(dprime_temp_different,.(session,subject2),summarize,mean=mean(prop_cor))
dprime_temp_different$condition <- "Hit"
dprime_temp5_7 <- rbind(dprime_temp_same,dprime_temp_different)

d_prime <- function(Hit,FA){
  qnorm(Hit) - qnorm(FA)
}

dprime_temp5_7 <- spread(dprime_temp5_7, condition, mean)

dprime_temp5_7 <- dprime_temp5_7 %>%
  group_by(session,subject2) %>%
  mutate(dprime = d_prime(Hit,FA))
dprime_temp5_7$stimulus <- "5-7"

dprime_id <- data.frame()
dprime_id <- rbind(dprime_temp1_3,dprime_temp2_4,dprime_temp3_5,dprime_temp4_6,dprime_temp5_7)
rm(dprime_temp_same,dprime_temp_different,dprime_temp1_3,dprime_temp2_4,dprime_temp3_5,dprime_temp4_6,dprime_temp5_7)

peak.discrim <- dprime_id %>% group_by(subject2,session) %>% slice(which.max(dprime))
peak.discrim <- select(peak.discrim,"session","subject2","dprime","stimulus")

# combine with category boundaries
load("boundaries.Rda")
boundaries$Boundary <- round(boundaries$Boundary)

# look at peak discrim token and boundaries
peak.discrim$boundary <- boundaries$Boundary
peak.discrim <- subset(peak.discrim,boundary!=-8)
ggplot(peak.discrim,aes(x=stimulus,y=boundary,color=stimulus,label=subject2)) + 
  scale_y_continuous('boundary',breaks=c(0:7)) +
  xlab('Peak discrimination stimulus') + geom_label_repel(aes(label=subject2))

# use this information to determine what is between-category and what is within-category
dprime_id$boundary <- NA
for (i in unique(dprime_id$subject2)){
  for (s in unique(dprime_id$session)){
    temp.boundaries <- boundaries[boundaries$subject2==i & boundaries$session==s,"Boundary"]
    dprime_id$boundary <- ifelse(dprime_id$subject2==i & dprime_id$session==s,temp.boundaries,dprime_id$boundary)
  }
}

dprime_id$discrim.type <- ifelse(dprime_id$boundary==0&dprime_id$stimulus=="3-5","BC","WC")
dprime_id$discrim.type <- ifelse(dprime_id$boundary==-8&dprime_id$stimulus=="3-5","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==1&dprime_id$stimulus=="1-3","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==2&dprime_id$stimulus=="1-3","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==3&dprime_id$stimulus=="2-4","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==4&dprime_id$stimulus=="3-5","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==5&dprime_id$stimulus=="4-6","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==6&dprime_id$stimulus=="5-7","BC",dprime_id$discrim.type)
dprime_id$discrim.type <- ifelse(dprime_id$boundary==7&dprime_id$stimulus=="5-7","BC",dprime_id$discrim.type)

dprime.relative.bound <- data.frame(matrix(vector(), 0, 9,
                                           dimnames=list(c(),c("session","subject2", "FA", "Hit","dprime",
                                                               "stimulus","boundary","discrim.type","relative.bound"))))

for (subj in unique(dprime_id$subject2)){
  for(ses in unique(dprime_id$session)){
    temp <- subset(dprime_id,subject2==subj&session==ses)
    B.C. = dprime_id[dprime_id$subject2==subj&dprime_id$discrim.type=="BC"&dprime_id$session==ses,"stimulus"]
    if (B.C.[1,1]=="1-3"){
      temp$relative.bound <- ifelse(temp$stimulus=="1-3"&temp$discrim.type=="BC","BC",
                                       ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC+1",
                                              ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC+2",
                                                     ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+3",
                                                            ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+4","")))))
    } else if (B.C.[1,1]=="2-4"){
      temp$relative.bound <- ifelse(temp$stimulus=="2-4"&temp$discrim.type=="BC","BC",
                                       ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-1",
                                              ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC+1",
                                                     ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+2",
                                                            ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+3","")))))
    } else if (B.C.[1,1]=="3-5"){
      temp$relative.bound <- ifelse(temp$stimulus=="3-5"&temp$discrim.type=="BC","BC",
                                       ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-2",
                                              ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC-1",
                                                     ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+1",
                                                            ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+2","")))))
    } else if (B.C.[1,1]=="4-6"){
      temp$relative.bound <- ifelse(temp$stimulus=="4-6"&temp$discrim.type=="BC","BC",
                                       ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-3",
                                              ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC-2",
                                                     ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC-1",
                                                            ifelse(temp$stimulus=="5-7"&temp$discrim.type=="WC","WC+1","")))))
    } else if (B.C.[1,1]=="5-7"){
      temp$relative.bound <- ifelse(temp$stimulus=="5-7"&temp$discrim.type=="BC","BC",
                                       ifelse(temp$stimulus=="1-3"&temp$discrim.type=="WC","WC-2",
                                              ifelse(temp$stimulus=="2-4"&temp$discrim.type=="WC","WC-1",
                                                     ifelse(temp$stimulus=="3-5"&temp$discrim.type=="WC","WC+1",
                                                            ifelse(temp$stimulus=="4-6"&temp$discrim.type=="WC","WC+2","")))))
    }
    temp <- as.data.frame(temp)
    dprime.relative.bound <- rbind(dprime.relative.bound,temp)
  }
}

dprime_rb_lineplot <- summarySE(dprime.relative.bound, measurevar="dprime",groupvars = c("session","relative.bound"))
dprime_rb_lineplot$relative.bound <- factor(dprime_rb_lineplot$relative.bound,levels=c("WC-3","WC-2","WC-1","BC","WC+1","WC+2","WC+3","WC+4"))
```

```{r,echo=FALSE,warning = FALSE,fig.width=8,fig.height=6}
ggplot(dprime_rb_lineplot,aes(x=relative.bound,y=dprime,group=session)) +
  geom_point(aes(color=session),stat='summary', fun.y='mean', size=3.5) +
  geom_line(aes(color=session),stat='summary', fun.y='mean', size=2) +
  geom_errorbar(aes(ymin=dprime-se,ymax=dprime+se,color=session),width=.25,size=1.25) +
  scale_color_brewer('Session',palette="Set1") +
  theme(text = element_text(size=20))
```

## Mixed effects model on d' with relative boundary:
```{r, echo = FALSE, message = FALSE, warning = FALSE}
dprime.relative.bound$session <- as.factor(dprime.relative.bound$session)
dprime.relative.bound$relative.bound <- as.factor(dprime.relative.bound$relative.bound)

lmem.relative.bound <- mixed(dprime ~ relative.bound*session + (session|subject2),data=dprime.relative.bound)
lmem.relative.bound
```

## Mixed effects model on d' with non-relative boundary (2-4 and 3-5 as BC):
```{r, echo = FALSE, message = FALSE, warning = FALSE}
dprime.relative.bound$nonrelative.bound <- ifelse(dprime.relative.bound$stimulus=="2-4"|dprime.relative.bound$stimulus=="3-5","BC","WC")

dprime.relative.bound$session <- as.factor(dprime.relative.bound$session)
dprime.relative.bound$nonrelative.bound <- as.factor(dprime.relative.bound$nonrelative.bound)

lmem.nonrelative.bound <- mixed(dprime ~ nonrelative.bound*session + (1|subject2),data=dprime.relative.bound)
lmem.nonrelative.bound
```

## Looking at change in boundaries over time:
```{r echo=FALSE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
# combine with category boundaries
load("boundaries.Rda")

# create figure before rounding boundaries
ggplot(boundaries,aes(x=session,y=Boundary,group=factor(subject2)),label=subject2) + 
  geom_point(size=3) +
  geom_line(aes(group=factor(subject2),color=factor(subject2)),size=1.5) +
  geom_label_repel(label=boundaries$subject2) +
  scale_color_discrete(guide=F) +
  ylim(0,7) +
  theme(text = element_text(size=20))
```

# Mixed effects model for boundary change over time:
```{r,include=FALSE}
# mixed effects model
bound.model <- mixed(Boundary ~ session + (1|subject2),data=boundaries)
```

```{r,echo=FALSE,message=FALSE,warning=FALSE}
bound.model
```